---
title: "The Ultraviolet Index is well estimated by the terrestrial irradiance at 310nm\nFigure 1"
author: "YouV Labs, Inc."
date: "1/22/2021"
output: pdf_document
---
```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 6, fig.height = 4)
library(tidyverse)
#library(latex2exp)
library(XML)
data_dir <- 'data'

#   ------------ helpers --------
eas <- function(lam){
  w <- lam
  w[lam>250 & lam <= 298] <- 1
  w[lam>298 & lam <= 328] <- 10^(0.094*(298-lam[lam>298 & lam <= 328]))
  w[lam>328 & lam <= 400] <- 10^(0.015*(139-lam[lam>328 & lam <= 400]))
  w[lam>400] <- 0
  return(w)
}

sdlam <- seq(286.5, 363, 0.5)
```

Figure 1 is a review of the standard atmosphere focused on ultraviolet wavelengths and the calculation of the UV Index (UVI).

### (a) The standard atmosphere AM0
ASTM G-173-03  is well described at https://www.nrel.gov/grid/solar-resource/spectra-am1.5.html, where we downloaded the relevant tables (https://www.nrel.gov/grid/solar-resource/assets/data/astmg173.xls) on November 11, 2020, and then converted to .csv by saving the astmg173 tab as .csv using Microsoft Excel.

```{r, load_astmg173}
astmg173 <- read.csv(paste(data_dir,"astmg173.csv",sep="/"), skip=1)
# units are nm, W/m2/nm, W/m2/nm, W/m2/nm
# note that the 'direct' column is only for light coming from the direction of the sun
# while the 'tilt' columm reports the total irradiance on a surface tilted away from the sun
names(astmg173) <- c('sdlam', 'Extraterrestrial','tilt','direct')
```

We also compare this astmg173 to the ISS solar spectral standard.


```{r atmosci_solar_data}
# -----------
#        SOLAR EMISSION SPECTRUM
# Meftah, Mustapha, et al. "SOLAR-ISS: A new reference spectrum based on SOLAR/SOLSPEC observations." 
# Astronomy & Astrophysics 611 (2018): A1.
#  This is the solar spectrum from space, not on the ground where varying conditions make for varying spectra
# http://bdap.ipsl.fr/voscat/SOLAR_ISS_V1.html
# -----------
r_solar <- paste(data_dir, "SOLAR_ISS_V1.Rdat", sep='/')
html_solar <- gsub('Rdat','html',r_solar)
if(!exists('sun_file')){
  if (!file.exists(r_solar)){
    sun_file <- htmlParse(html_solar)
    sun_nodes <- getNodeSet(sun_file, "//table")
    sun <- readHTMLTable(sun_nodes[1][[1]], colClasses = c("numeric", "numeric", "numeric"),
                         headers = c("wavelength", "SSI", "Uncertainty"), stringsAsFactors = FALSE)
    names(sun) <- c("wavelength", "SSI", "Uncertainty")
    sun <- sun[!is.na(sun$wavelength), ]
    save(sun, file=r_solar)
  } else {
    load(r_solar)
  }
  sun_uv <- sun[sun$wavelength >= min(sdlam) & sun$wavelength <= 400, ]
}

plot(sun_uv$wavelength, sun_uv$SSI, type="l", xlab="Wavelength (nm)", ylab="Irradiance (W/m2/nm)", main="ISS Solar Irradiance Above Atmosphere \n ASTM G-173 Extraterrestrial Irradiance")
points(c(310, 310), c(0,2), type="l", lwd=1.5)
lines(astmg173$sdlam, astmg173$Extraterrestrial, col="red")
```

They are well matched, the ISS spectrum is reported with finer spectral resolution.

### (b) Loss in transit, ozone absorption cross section

Light from the sun suffers two main losses as it passes through the atmosphere,
aerosol loss or scattering away due to stuff, mostly water droplets, found in the atmosphere,
and absorption due to the molecules floating in the atmosphere, mostly ozone.


```{r ozone_load}
#
#  from http://igaco-o3.fmi.fi/ACSO/cross_asections.html
#  ref http://www.atmos-meas-tech.net/6/3055/2013/amt-6-3055-2013.pdf
fname <- paste(data_dir,'SCIA_O3_Temp_cross-section_V4.1.DAT',sep="/")

col.names <- c("wavelength", "O3_203", "O3_223", "O3_243", "O3_273", "O3_293")
o3 <- read.table(fname, skip = 21, col.names = col.names)

plot(o3$wavelength[o3$wavelength>305 & o3$wavelength<400], 1e22 * o3$O3_273[o3$wavelength>305 & o3$wavelength<400], type="l", col="blue", xlab="Wavelength", ylab="Cross Section * 10^22 (cm2/molecule)", log="y")

lines(o3$wavelength[685], o3$O3_273[685], type="p", col="blue")
```

### (c) AM1.5 Irradiance on the ground

The ASTM standard irradiance spectrum is for a spot on the northern hemisphere of the earth tilted at 37 degrees from the direct normal when the equivalent ozone layer is 340 Dobson Units (0.34cm) and with a particular set of 33 atmospheric layers.
This is too complicated for our purposes.
We instead look at the spectrum on earth and try to build it out of aerosol loss,
the simple huber approximation for the wavelength dependence of rayleigh scattering,
and ozone absorption.

```{r matchatm}
du  <- 340
ray <- -55e-4
aer <- 0.83
indices <- astmg173$sdlam>280 & astmg173$sdlam<=400
irsimp <- data.frame(sdlam = astmg173$sdlam[indices],
                     Extraterrestrial = astmg173$Extraterrestrial[indices],
                     tilt = astmg173$tilt[indices],
                     direct = astmg173$direct[indices])
plot(irsimp$sdlam, irsimp$tilt, type="l", 
     xlab="Wavelength (nm)", ylab="Irradiance (W/m2/nm)")
o3cx = approx(o3$wavelength, o3$O3_273, 
              xout=irsimp$sdlam)$y
irsimp$huber <- irsimp$Extraterrestrial * exp(-du * o3cx / 3.721e-17 / sin(37*pi/180) ) * exp(-aer) * exp(-ray*(irsimp$sdlam-320))
irsimp$huber_direct <- irsimp$Extraterrestrial * exp(-du * o3cx / 3.721e-17) * exp(-aer/sin(37*pi/180)) * exp(-ray*(irsimp$sdlam-320))
lines(irsimp$sdlam, irsimp$huber, col="red", lty=2)
```

Frankly, that isn't bad.
It is a bit heuristic in that the two numbers `r aer` and `r ray` are unlikely
to be correct, but the model does capture the spirit of the physics without
getting bogged down in issues critical to other applications such as 
the angular distribution of incoming light.


### (d) The Erythema Action spectrum

The EAS is the health weighting of each wavelength.

```{r eas}
plot(irsimp$sdlam, eas(irsimp$sdlam), log="y", xlab="Wavlength (nm)", ylab="Relative skin sensitivity", type="l", lwd=2)
```

### (e) Damage vs wavelength 

The resulting standard skin damage spectrum is

```{r ssxeas}
plot(irsimp$sdlam, eas(irsimp$sdlam)*irsimp$tilt/.5, xlab="Wavlength (nm)", ylab="Erythemal Irradiance W/m2/nm", type="l", lwd=2)
uvis <- sum(eas(irsimp$sdlam)*irsimp$tilt)*25/.5
```

### Final Figure


Saved by this code, displayed in the paper, not here.

```{r uviexplain, width=7, height=10.5}
figsave <- TRUE
if (figsave){
mag<-3 } else {mag <- 1}
cextitle <- 1.5*mag
if(figsave){
  png(filename="fig1expl.png", width=mag*340, height=mag*510)
} # else {figsave=TRUE}
par(mfrow=c(5,1), mar=c(0,4.1,.2,4.1)*mag, cex=1.25*mag)
layout(matrix(1:5), heights=c(0.8, 0.8 ,0.8, 0.8, 1.3))

#---------------------------------------(a)-------------------------------------------
plot(astmg173$sdlam, astmg173$Extraterrestrial, type="l", xaxt="n", ylab="", yaxt="n", lwd=1.5*mag, xlim=c(280,400))
points(310, astmg173$Extraterrestrial[astmg173$sdlam==310], type="p", lwd=2*mag, col="blue", cex=mag)
text(285,1.6,"(a) Irradiance above the atmosphere", adj=0, cex=cextitle)

#----------------------------------------(b)------------------------------------------
par(mar=c(0,4.1,0,4.1)*mag)
plot(o3$wavelength[o3$wavelength>280 & o3$wavelength<400], 
     o3$O3_273[o3$wavelength>280 & o3$wavelength<400], type="l", col="blue",
     lwd=1.5*mag,
     xaxt="n", yaxt="n", log="y", ylab="")
text(285,2e-23, "(b) Ozone absorption (Log)", adj=0, cex=cextitle)
points(o3$wavelength[685], o3$O3_273[685], lwd=mag, type="p", col="blue", cex=mag)

#-----------------------------------------(c)-----------------------------------------
plot(irsimp$sdlam, irsimp$tilt/.5, xaxt="n", yaxt="n", type="l", lwd=2*mag, ylab="")
points(310,irsimp$tilt[irsimp$sdlam==310]/.5, col="blue", cex=mag, lwd=2*mag)
lines(irsimp$sdlam, irsimp$huber/.5, col="red", lty=3, lwd=2.3*mag)
text(285,1.75,"(c) Irradiance under atmosphere", adj=0, cex=cextitle)
legend(x=c(370, 390), y=c(0.1, 0.8), lty=c(1, 3), lwd=2.3 * mag, legend=c("AM1.5", "Model"),
       col=c("black","red"), cex=0.75*cextitle, bty="n")
#------------------------------------------(d)----------------------------------------
plot(irsimp$sdlam, eas(irsimp$sdlam), log="y", xaxt="n", yaxt="n", ylab="", type="l", 
     col="blue", lwd=2*mag, ylim=c(1e-4,2))
points(310,eas(310), col="blue", lwd=2*mag, cex=mag)
text(340,.1,"(d) Relative erythemal\n     sensitivity (Log)", adj=0, cex=cextitle)

#------------------------------------------(e)----------------------------------------
par(mar=c(5,4.1,0,4.1)*mag)
plot(irsimp$sdlam, eas(irsimp$sdlam)*irsimp$tilt/.5 , type="l", lwd=2*mag, col="red",
     cex.axis=mag, xaxt="n", ylab="", xlab="", yaxt="n")
polygon(c(irsimp$sdlam, 2800), c(eas(irsimp$sdlam) * irsimp$tilt / 0.5, 0), col="pink", border=NA)
points(310,eas(310)*irsimp$tilt[irsimp$sdlam==310]/.5, col="blue", lwd=mag, cex=mag)

axis(side="1", cex.axis=1.25*mag)
title(xlab="Wavelength(nm)", line=5, cex.lab=1.5*mag)
text(340, 0.006,"(e) Erythema weighted\n     irradiance", adj=0, cex=cextitle)
text(307, 0.0035,"UVI", adj=0, cex=cextitle)

#-------------------------ozone inset----------------------------------------------
par(fig=c(0.66, 1, .68, 0.82), new = T, mar=c(2,0,0,4.1)*mag)
plot(o3$wavelength[o3$wavelength>305 & o3$wavelength<315], 
     1e22 * o3$O3_273[o3$wavelength>305 & o3$wavelength<315], type="l", col="blue",
     yaxt="n", xaxt="n", xlab="", log="y", ylab="", lwd=2*mag, 
     cex.axis=cextitle*1.5)
points(o3$wavelength[685],1e22 * o3$O3_273[685], type="p", col="blue", lwd=mag, cex=mag, cex.axis=mag)

#----------------------------------------------------------------------------------
axis(1,cex.axis=1.5)
if (figsave){ dev.off() }
```

Figure 1.