---
title: "The Ultraviolet Index is well estimated by the terrestrial irradiance at 310nm\nFigure 3"
author: "YouV Labs, Inc."
date: "1/22/2021"
output: pdf_document
---

Let's make a simple tool to make a publication quality figure with the grahical derivation of the 310nm result. 

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(latex2exp)
library(limSolve)
data_dir <- 'data'

#   ------------ helpers --------
eas <- function(lam){
  w <- lam
  w[lam>250 & lam <= 298] <- 1
  w[lam>298 & lam <= 328] <- 10^(0.094*(298-lam[lam>298 & lam <= 328]))
  w[lam>328 & lam <= 400] <- 10^(0.015*(139-lam[lam>328 & lam <= 400]))
  w[lam>400] <- 0
  return(w)
}

lambda <- seq(286.5,363,0.5)
```

## Andover graphical derivation

We begin by loading a dataset.

```{r datasets}
uvnet_path <- '/Volumes/GoogleDrive/Shared drives/Research/Data science/Monte Carlo simulation for diode evaluation/UVnet (EPA)'  # set to 'data' for most users
uvnet_sites <- c("Acadia NP ME", "Albuquerque NM", "Boulder CO", "Canyonlands NP UT",
                 "Chicago IL", "Gaithersburg MD", "Research Triangle Park NC",
                 "Riverside CA", "Big Bend TX")
uvnet_files <- paste(uvnet_path, uvnet_sites, uvnet_sites, sep="/")
uvnet_files <- uvnet_files %>% paste0(".RData")
```

And then we select a day and location for the figure. If you want a different choice, change the values in this chunk.

```{r select_day_date}
dset <- 1   # change these three variables to sample the data set on a different day or location
day <- 173  #  for Acadia, summer solstice (June 21,2000) select [dset=1, day=173, year=2000]
year <- 2000
```

We chose `r uvnet_files[dset]`. 

And then find all the spectra from the `r day`th day in `r year`.

```{r loadset}
load(uvnet_files[dset])  #  loads: data_file_info[date, qc info, location, instrument], scans_info[scan #, solar zenith, hour, spec_name], spectra[matrix of irradiance values]
rowfilter <- duplicated(scans_info)
lam <- gsub("nm", "", colnames(spectra)) %>% as.numeric
easv <- eas(lam)
scans_info$uvi <- spectra %*% easv * 0.5 / 25
uvimin <- 0.01
uvimax <- 15
rowfilter <- rowfilter | scans_info$uvi <= uvimin | scans_info$uvi >= uvimax
scans_info <- scans_info[!rowfilter,]
spectra <- spectra[!rowfilter,]
days <- gsub('s.*$','',scans_info$spec_name) %>% unique
```


There are `r nrow(scans_info)` unique spectra with uvi from `r uvimin` to `r uvimax` collected from `r uvnet_sites[dset]`.

```{r}
day_scans <- function(year = 1999, day = 180, location="Acadia NP", select_scans = c(), maxI=60, 
                      norm="uvi", tstring="default", 
                      uvimin=0, irrad_weight="both", cex=1.0)
{
  if (length(select_scans) > 0){
    snames <- scans_info$spec_name[select_scans]
    sindices <- which(select_scans)
  } else
  {
    snames <- scans_info$spec_name
    sindices <- 1:nrow(scans_info)
  }
  # ------------------------- x and y axis labels ---------------------
  if (norm == "uvi"){
    ylab = ""
    xlab = "Wavelength (nm)"
  } else if (norm == "andover")
  {    ylab = ""} else
  {
    ylab=""
    xlab=""
  }
  default_title <- paste(location, strftime(strptime(paste0(year,day), format="%Y%j"), format="%b %d, %Y"), sep=" ")
  if (tstring == "default") {
    tstring <- default_title
  }
  # ------------------------plot box--------------------------------------------
  plot(c(293, 363), c(0, maxI), pch=".", ylab=ylab, xlab=xlab, yaxt="n",
       main=tstring, cex.axis=cex, cex.lab=cex, xaxt="n")
  # ------------------------annotation------------------------------------------
  if (norm == "uvi"){ 
    axis(1, cex.axis=0.8*cex)
    if (irrad_weight == "erythema"){
            axis(2, cex.axis=0.8*cex)
            text(320, maxI*.9, adj=0, "(c) Erythemal Irradiance / UVI", cex=cex)
          } else  {
        text(325, maxI*.9, adj=0, "Irradiance / UVI", cex=cex)
          }
  } else 
  {
    if (irrad_weight == "erythema"){
      axis(4, cex.axis=0.8*cex)
      text(320, maxI*.9, adj=0, "(b) Erythemal Irradiance", cex=cex)
    } else  {
      axis(2, cex.axis=0.8*cex)
      text(293, maxI*.9, adj=0, "(a) Irradiance", cex=cex)
    }
  }
  # ------------------------------------ plot spectral data -------------------------
  for (i in sindices){
    if(scans_info$uvi[i] > uvimin){
    if (norm == "uvi"){
      if (irrad_weight == "erythema"){
        lines(lam, (easv * spectra[i,])/(spectra[i,] %*% easv*.5/25)[1], col="red" )
      } else {
        lines(lam, spectra[i,] / (spectra[i,] %*% eas(lambda) * 0.5 / 25)[1] )
      }
    } else {
      if (irrad_weight == "erythema"){
        lines(lam, easv * spectra[i, ], col="red" )
      } else{
        lines(lam, spectra[i, ])
      }
    }
    }
  }
  lines(c(310, 310), c(0,0.8 * maxI), col="blue", lwd=2)
# -------------------------------inset-------------------------
  if (norm == "uvi" & irrad_weight=="erythema"){
    bx = c(300, 315)
    by = c(0.7, 1.8)
    lines(c(bx[1], bx[2], bx[2], bx[1], bx[1]), c(by[1], by[1], by[2], by[2], by[1]))
    mar=par("mar")  # store settings
    fig=par("fig")
    par(fig=c(0.5, 0.9, 0.18, 0.3), mar=c(0, 0, 0, 0), new=TRUE)
    plot(c(bx[1], bx[2]), c(by[1], by[2]), pch=".", ylab="", xlab="", yaxt="n", xaxt="n")
    for (i in sindices){
      if(scans_info$uvi[i] > uvimin){
        lines(lam, easv * spectra[i,]/(spectra[i,] %*% easv * 0.5 / 25)[1], col="red" ) 
      }
    }
    lines(c(309.5,309.5), c(by[1],by[2]), lwd=2, col="blue")
    lines(c(310.5,310.5), c(by[1],by[2]), lwd=2, col="blue")
    par(fig=fig, mar=mar, new=FALSE) # restore settings
  }
}

day_3fig <- function(year = 1999, day = 180, location="Acadia NP", select_scans = c(), uvimin=0.1, cex=1.5)
{
  par(mfrow=c(3,1), mar=c(0,3.3,0.5,3.3))
  layout(matrix(1:3), heights=c(1, .85 ,1.15))
  day_scans(year=year, day=day, location=location, select_scans=select_scans, norm="none", 
            maxI=max(spectra[select_spectra, ])*1.05, uvimin=uvimin, tstring="", irrad_weight="raw", cex=cex)
  par(mar=c(0,3.3,0,3.3))
  es <- apply(spectra[select_spectra, ],1,function(x) x*easv)
  day_scans(year=year, day=day, location=location, select_scans=select_scans, norm="none", 
            maxI=max(es*1.05), uvimin=uvimin, tstring="", irrad_weight="erythema", cex=cex)
  par(mar=c(8,3.3,0,3.3))
  
  day_scans(year=year, day=day, location=location, select_scans=select_scans, norm="uvi", 
            maxI=max(es/max(scans_info$uvi[select_scans])), tstring="", uvimin=uvimin,
            irrad_weight="erythema", cex=cex)
}
```

```{r subset, fig.width=8, fig.height=9}
figsave=FALSE
#select_spectra <- grepl(paste0("[:alpha:]",year,day), scans_info$spec_name)

select_spectra <- grepl(paste0(year,day,"s"), scans_info$spec_name)
scans_used <- scans_info[select_spectra, ]
spectra_used <- spectra[select_spectra, ]
if(figsave){  png(filename="fig2derive.png", width=700, height=1020) }

day_3fig(year=year, day=day, location=uvnet_sites[dset], select_scans = select_spectra, uvimin=.5, cex=3)

if(figsave){  dev.off()  }
```

Graphical derivation of the 310nm result. 
Irradiance units are $W/m^2/nm$ and the UVI normalized units are $W/m^2/nm/UVI$. 
Erythema weighted curves (red) are multiplied by 200. 
Plotted data are all spectra with UVI > 0.5 taken at 
`r paste(uvnet_sites[dset],"on", strftime(strptime(paste0(year,day), format="%Y%j"), format="%b %d, %Y"), sep=" ")`.

